Scaffolder - Simple and reproducable genome scaffolding using text configuration files.

### 2011-01-11 text/src/article.tex
Set abstract sections
Fix address

\address{\iid(1) Department of Biological Sciences, Northern Kentucky%
University, SC 204D Nunn Drive, Highland Heights, KY 41076 }%

\maketitle
%}}}
% {{{ Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The Abstract begins here                 %%
%%                                          %%
%% The Section headings here are those for  %%
%% a Research article submitted to a        %%
%% BMC-Series journal.                      %%  
%%                                          %%
%% If your article is not of this type,     %%
%% then refer to the Instructions for       %%
%% authors on http://www.biomedcentral.com  %%
%% and change the section headings          %%
%% accordingly.                             %%   
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
        % Do not use inserted blank lines (ie \\) until main body of text.
        \paragraph*{Background:} Text for this section of the abstract.

        \paragraph*{Results:} Text for this section of the abstract \ldots

        \paragraph*{Conclusions:} Text for this section of the abstract \ldots
\end{abstract}

>>>>

\address{\iid(1) Department of Biological Sciences, Northern Kentucky%
University, Nunn Drive, Highland Heights, KY 41076 }%

\maketitle
%}}}
% {{{ Abstract

\begin{abstract}
  \paragraph*{Background:} Background \dots
  \paragraph*{Methods:} Methods \dots
  \paragraph*{Results:} Results \ldots
  \paragraph*{Conclusions:} Conclusions \ldots
\end{abstract}
